Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-10-07 paper.tex
ref response 5: correct 200% -> 100%

Because the model was evolved with a gray M1 transport scheme,
the only \emph{scat} method we can use in our ray tracing is the
\emph{gray} method.
As in the post-bounce configuration in Sec.~\ref{ssec:test_collapse},
the \emph{scat} treatment is more faithful than the \emph{noscat} treatment,
significantly so for the heavy-lepton neutrinos.
For example, with scattering turned off the ray tracing and M1 measurements
of $L_{\nu_x}$ disagree by 200\%;
but with scattering turned on agreement is within 10\%.
As the ray tracing and M1 measurements both show,
$R_{\bar{\nu}_e}$ dominates over $R_{\nu_e}$ significantly,
because the disrupted neutron star material is releptonizing.

>>>>

Because the model was evolved with a gray M1 transport scheme,
the only \emph{scat} method we can use in our ray tracing is the
\emph{gray} method.
As in the post-bounce configuration in Sec.~\ref{ssec:test_collapse},
the \emph{scat} treatment is more faithful than the \emph{noscat} treatment,
significantly so for the heavy-lepton neutrinos.
For example, with scattering turned off the ray tracing and M1 measurements
of $L_{\nu_x}$ disagree by 100\%;
but with scattering turned on agreement is within 10\%.
As the ray tracing and M1 measurements both show,
$R_{\bar{\nu}_e}$ dominates over $R_{\nu_e}$ significantly,
because the disrupted neutron star material is releptonizing.
